BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-15 tex/3-algorithms.tex
algo++

This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments. We will see how blog specific characteristics can be exploited to obtain an extraction procedure applicable to all posts of a blog. A careful attention will be paid to minimizing algorithmic complexity while keeping the simple and general approach of the algorithm.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
- getting content from HTML is not easy.
\cite{worldwidewebconsortiumw3c2002}

% Assumptions when working with blogs
\Anotecontent{assumptions}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}
Working with blogs allows to make assumptions\Anote{assumptions} that are central in our extraction procedure:
\begin{enumerate}
  \item Web feeds provide a structured and standardized view of the most recent posts
  \item Posts of a same blog share the similar HTMP structure.
\end{enumerate}

% Web feeds limitations
In average, web feeds only contain about 20 entries \cite{french paper} which is generally lower than the total number of posts in a blog. In order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed. The algorithm we are going to present in this section as for function to build wrappers for the relevant data of blog posts, which are going to be use

% Per blog procedure, inputs/output
Each time a new crawl is initiated our system builds a set of wrappers that are then used for the entirety of the blog. With this wrappers in hands, extraction data from the HTML page of a blog post is nothing more than parsing the HTML page running each XPath query, which can all by done with the standard python library \footnote{lxml, beautifullsoop}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
- related algorithms, general brute force viewpoint
- algorithm
- XPath selectors (id, else class, else path)
- string similarity
- caching

>>>>

This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments. We will see how we can take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog. A careful attention will be paid to minimizing algorithmic complexity while keeping the approach simple and general.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% HTML extraction is non trival
Extracting metadata and content from HTML is not easy. Standards and recommendations have been present for quite some time, and tend to be quite strict on how the HTML documents should be organized. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not be used more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}. In fact, a majority of web designer rely on the generic \code{<span></span>} and \code{<div></div>} containers with a custom \code{class} or \code{id} attributes to organize HTML pages. Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.

% Assumptions when working with blogs
\Anotecontent{noteA}{We observed during evaluation that all failing test blogs where violating one of these assumptions.}

Working with blogs allows to make assumptions\Anote{noteA} that will be central in our extraction procedure:
\begin{enumerate}[label={(\arabic*)}]
  \item \label{havefeed} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
  \item \label{similarhtml} Posts of a same blog share a similar HTML structure.
\end{enumerate}
On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog. In order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
% \Anotecontent{vague}{The definition of the objective extraction rule is voluntarily vague, }

% Per blog procedure, inputs/output
The algorithm we are going to present in this section as for function to build an extraction rule for a relevant data of blog posts. It takes an input a set of pairs of HTML pages and target contents, and returns a extraction rule. The extraction rule should be such that when applied to one of the page, it will return data close to the target content of the corresponding page.

input : A set $pageZipTarget$ of Html page and Text target pairs
output: Best extraction rule
Q <- empty list
foreach (page, target) \in pageZipTarget do
  Q <- Q + BestExtractionRule(page, target)
return the extraction rule with highest occurrence in Q

ALGO1.

Given a blog, the crawler can use assumption \ref{havefeed} to obtain inputs for ALGO1. Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page. Assumptions \ref{similarhtml} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs. \ref{similarhtml} is also key to ensure applicability of the rule to all posts of the blog.

2

- related algorithms, general brute force viewpoint
- algorithm
- XPath selectors (id, else class, else path)
- string similarity
- caching

### 2013-11-15 tex/4-techniques.tex
algo++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: blog-post identification and download priority heuristic. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data. that will then be taken it into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

\Anotecontent{commentfeed}{Blogs that do not provide a global comment feed need a special handling. If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost. However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{commentfeed} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably. Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

\Anotecontent{noteC}{Blogs that do not provide a global comment feed need a special handling. If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost. However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably. Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

### 2013-11-15 tex/main.tex
Back to archi after discussion with Nicos.
Algorithms assumptions.
Back to techniques instead of architecture.
Progress...
Fix some text on techniques, add image with scrapy architecture.
Techniques done.
algo++

\usepackage{epsfig}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{hyperref}

\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}

@@

% \title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
\title{BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web}
% to Extract Data From the Modern Web}
% Modern Web Pages}

@@

\author{
% 1st. author
\alignauthor
Olivier Blanvillain\\
       \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
       \affaddr{1014 Lausanne, Switzerland}\\
       \email{olivier.blanvillain@epfl.ch}
% 2nd. author
\alignauthor
Nikos Kasioumis\\
       \affaddr{European Organization for Nuclear Research (CERN)}\\
       \affaddr{1211 Geneva 23, Switzerland}\\
       \email{nikos.kasioumis@cern.ch}
% 3rd. author
\alignauthor
Vangelis Banos\\
       \affaddr{Department of Informatics}\\
       \affaddr{Aristotle University of Thessaloniki, Greece}\\
       \email{vbanos@gmail.com}
}

\maketitle
\begin{abstract}
\input{0-abstract.tex}
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\input{1-intro.tex}
\input{2-related-work.tex}
\input{3-architecture.tex}
\input{4-algorithms.tex}
\input{5-evaluation.tex}
\input{6-conclusion-and-future-work.tex}

\bibliographystyle{abbrv}
\bibliography{sigproc}
\end{document}

>>>>

\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{quoting}
\usepackage{url}
\usepackage{sepfootnotes}

\newfootnotes{A}
\MakeOuterQuote{"}
\quotingsetup{vskip=0pt,font={itshape}}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}

@@

  \title{BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs}

@@

  \author{
  % 1st. author
  \alignauthor
  Olivier Blanvillain\\
         \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
         \affaddr{1014 Lausanne, Switzerland}\\
         \email{\surl{olivier.blanvillain@epfl.ch}}
  % 2nd. author
  \alignauthor
  Nikos Kasioumis\\
         \affaddr{European Organization for Nuclear Research (CERN)}\\
         \affaddr{1211 Geneva 23, Switzerland}\\
         \email{\surl{nikos.kasioumis@cern.ch}}
  % 3rd. author
  \alignauthor
  Vangelis Banos\\
         \affaddr{Department of Informatics}\\
         \affaddr{Aristotle University of Thessaloniki, Greece}\\
         \email{\surl{vbanos@gmail.com}}
  }

  \maketitle

  \begin{abstract}
    \input{0-abstract.tex}
  \end{abstract}

  % % A category with the (minimum) three required fields
  % \category{H.4}{Information Systems Applications}{Miscellaneous}
  % %A category including the fourth, optional field follows...
  % \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

  \terms{Algorithms, Software Engineering}

  \keywords{Web archiving, Web crawling, ...}

  \input{1-intro.tex}
  \input{2-related-work.tex}
  \clearpage
  \input{3-algorithms.tex}
  \clearpage
  \input{4-techniques.tex}
  \clearpage
  \input{5-evaluation.tex}
  \clearpage
  \input{6-conclusion-and-future-work.tex}

  \bibliographystyle{abbrv}
  \bibliography{main}

\end{document}
